\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\name{Aleksei}{Nemtyrev}
\address{K553, Warandelaan 2}{5037 AB Tilburg, The Netherlands}
\phone[mobile]{+31 6 2305 6167}
\email{a.nemtyrev@tilburguniversity.edu}

%====================
\begin{document}
%====================

\makecvtitle

\section{Profile}
PhD student in Economics at Econometrics and Operations Research Department at Tilburg University.Strong background in econometrics, macroeconomics and monetary economics. 

\section{Education}
\cventry{2023--Present}{PhD, EOR Department}{University of Tilburg}{Tilburg, Netherlands}{}{}
\cventry{2021--2023}{Research Master's, Economics}{University of Tilburg}{Tilburg, Netherlands}{}{CentER scholarship holder}
\cventry{2020--2021}{MSc, Economics}{University of Amsterdam}{Amsterdam, Netherlands}{}{Track: Monetary Policy and Banking, Amsterdam Merit Scholarship holder}
\cventry{2012--2016}{MA, Economics}{University of Glasgow}{Glasgow, United Kingdom}{}{}

\section{Research Experience}
\cventry{Sep 2022--Aug 2023}{Research Assistant to Prof. Otilia Boldea}{Tilburg University}{Tilburg, Netherlands}{}{
\begin{itemize}
  \item Research project on smoothing local projections.
\end{itemize}}

\cventry{May 2022--Aug 2022}{Research Assistant to Prof. Jeffrey Campbell}{Tilburg University}{Tilburg, Netherlands}{}{
\begin{itemize}
  \item Project on recovery from natural disasters, application of Kalman filters.
\end{itemize}}

\section{Teaching Experience}
\cventry{Sep 2023--Present}{Teaching Assistant}{Tilburg University}{Tilburg, Netherlands}{}{
\begin{itemize}
  \item Statistics 2 – BSc International Business Administration
  \item Data Science Methods – MSc Econometrics and Mathematical Economics
\end{itemize}}

\section{Skills}
\cvitem{Programming}{Python, R, MATLAB, LaTeX, Stata}
\cvitem{Quantitative}{Time-series econometrics, Macroeconomics}
\cvitem{Languages}{English (Advanced), Russian (Native), Dutch (Beginner)}

%====================
\section*{Work in Progress}
%====================

\vspace{0.5em}

\cvitem{1}{\textbf{“Targeted Local Projections”} \\
Joint work with Otilia Boldea. }

\cvitem{2}{\textbf{“DSGE Modeling and Estimation”} \\
Joint work with Jeffrey Campbell.}

\cvitem{3}{\textbf{“Improving FOMC Policy with Credit Spreads”} \\
Joint work with Jeffrey Campbell.}

\section{Industry Experience}
\cventry{Jul 2016--Jul 2020}{Manager}{NEVA Torg Ltd.}{St. Petersburg, Russia}{}{
}

\end{document}